### 2008-08-29 htdocs/sections.tex
Added porous media section correction.
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@407 40876441-3496-0410-a613-a2fca35b2ae2

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  sections.tex
%
%  Content for Ludwig documentation.
%
%  $Id: sections.tex,v 1.3 2008-08-29 09:28:08 kevin Exp $
%
%  Edinburgh Soft Matter and Statistical Physics Group and
%  Edinburgh Parallel Computing Centre
%
%  Kevin Stratford (kevin@epcc.ed.ac.uk)
%  (c) 2008 The University of Edinburgh
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Single fluid permeability calculations for a given proous structure
can be undertaken by driving a flow via the fluid body force. Note
that the structure must be periodic in the direction of the force
(this may mean duplicating a 'reflected' version of a given sample
to create the correct input). The body force can be specified so
that, e.g., to drive a flow in the $x-$direction

@@

Note that in the case of porous media with narrow channels at the grid
scale, the wall velocity can be dependent on the viscosity of the fluid.
This is an artefact of the bounce-back on links and will result in a
viscosity-dependent permeability (see, e.g., \cite{lipanmiller}). To minimise
this effect, it is recommended to to on the correction to the ghost
mode relaxation time proposed by Ginzburg and d'Humi\`eres \cite{ginzburg}
which corrects the viscosity-dependence of the apparent boundary
position. This is done via the input switches

@@

and should recover a viscosity-independent premeability measurement
\cite{lipanmiller,chunladd}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  sections.tex
%
%  Content for Ludwig documentation.
%
%  $Id: sections.tex,v 1.4 2008-08-29 09:32:59 kevin Exp $
%
%  Edinburgh Soft Matter and Statistical Physics Group and
%  Edinburgh Parallel Computing Centre
%
%  Kevin Stratford (kevin@epcc.ed.ac.uk)
%  (c) 2008 The University of Edinburgh
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Single fluid permeability calculations for a given proous structure
can be undertaken by driving a flow via the fluid body force. Note
that the structure must be periodic in the direction of the force
(this may mean duplicating a 'reflected' version of a given sample
to create the correct input). The body force can be specified so
that, e.g., to drive a flow in the positive $x-$direction

@@

Note that in the case of porous media with narrow channels at the grid
scale, the wall velocity can be dependent on the viscosity of the fluid.
This is an artefact of the bounce-back on links and will result in a
viscosity-dependent permeability (see, e.g., \cite{lipanmiller}). To minimise
this effect, it is recommended to switch on the correction to the ghost
mode relaxation time proposed by Ginzburg and d'Humi\`eres \cite{ginzburg}
which corrects the viscosity-dependence of the apparent boundary
position. This is done via the input switches

@@

and should recover a viscosity-independent permeability measurement
\cite{lipanmiller,chunladd}.
